---
title: "Enterprise {gtsummary}"
subtitle: "Themes, ARDs, and Custom Extensions for Pharma"
author: "Daniel D. Sjoberg and Shannon Pileggi"
event: "R/Pharma 2026"
hero-logo: "../images/gtsummary-logo.png"
avatars:
  - src: "../images/dan-circle.png"
    alt: "Headshot of Daniel Sjoberg"
  - src: "../images/shannon-pileggi-circle.png"
    alt: "Headshot of Shannon Pileggi"
logo: "../images/gtsummary-logo.png"
footer:  "[Enterprise {gtsummary}: Themes, ARDs, and Custom Extensions for Pharma](https://ddsjoberg.github.io/rpharma-workshop-gtsummary-adoption-2026/)"
editor: source
engine: knitr
format:
  revealjs:
    theme: ../slides.scss
    template-partials:
      - ../title-slide.html
    transition: fade
    slide-number: true
    chalkboard: true
execute:
  echo: true
  message: true
  freeze: false
cache: false
---

```{r}
#| label: setup-options-gtsummary
#| echo: false
options(width = 120)
```

{{< include ../gtsummary/00-setup.qmd >}}

# Analysis Results Datasets

```{r}
#| label: setup-options-ard
#| echo: false
# ARD tibbles are wide; give them room and cap the printed rows
options(width = 200)
options(pillar.print_max = 10, pillar.print_min = 10)
```

{{< include ../ard/intro_to_ards.qmd >}}

{{< include ../ard/cards.qmd >}}

```{r}
#| label: reset-options-gtsummary
#| echo: false
options(width = 120)
```

# {gtsummary} fundamentals

{{< include ../gtsummary/01-background.qmd >}}

{{< include ../gtsummary/02-tbl_summary.qmd >}}

{{< include ../gtsummary/03-tbl_hierarchicial.qmd >}}

{{< include ../gtsummary/04-tbl_merge.qmd >}}


## Break ☕

::: {.small}
[Covered so far: Analysis Results Datasets · {gtsummary} fundamentals]{.muted}
:::

### Up next

::: {.small}

3.  [ARD-first tables]{.emphasis} — every cell traceable, and QC by comparing one ARD against another.

4.  [Print engines]{.emphasis} — {gt}, {flextable}, and submission-ready Word output.

5.  [Adopting {gtsummary}]{.emphasis} — a house theme, wrappers of your own, and {crane}.

6.  [Coding agents]{.emphasis} — writing your standards down so an agent follows them without being reminded.

:::

```{r}
#| label: break-countdown
#| echo: false
#| cache: false
countdown::countdown(minutes = 10, play_sound = TRUE)
```

{{< include ../gtsummary/05-ard-first.qmd >}}

{{< include ../gtsummary/06-print_engines.qmd >}}

{{< include ../gtsummary/07-adopt.qmd >}}

{{< include ../gtsummary/08-coding-agents.qmd >}}

{{< include ../gtsummary/09-summary.qmd >}}
